Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-17 chi2012.tex
minor edit

The information in Table \ref{tbl:data} summarizes the metrics that were captured of the trials for each participant. We analyze this data next.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=8.5cm]{img/results}
\caption{The chosen restaurant/university for each participant, showing the choice on the x axis and frequency on the y axis under conditions A and B.}
\label{fig:results}
\end{center}
\end{figure}

>>>>

The information in Table \ref{tbl:data} summarises the metrics that were captured of the trials for each participant. We analyse this data next.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=8.5cm]{img/results}
\caption{The chosen restaurant/university for each participant, showing the choice on the x axis and frequency on the y axis under conditions A (blue) and B (red).}
\label{fig:results}
\end{center}
\end{figure}
